Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-22 paper/paper.tex
pass table iii and table iv

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 4 \\
    2100384 & 13 & 8 & 18 & 2 \\
    2100399 & 132 & 6 & 3 & 1 \\
    2100401 & 12 & 6 & 25 & 1 \\
    2100402 & 3 & 6 & 12 & 1 \\
    2100408 & 15 & 8 & 9 & 2 \\
    2100485 & 4 & 6 & 3 & 1 \\
    2100486 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 34 & 3\\
    iisadmin access & 3 & 17 & 408 & 1 \\        
    JBoss JMX & 5 & 23 & 228 & 45 \\
    scripttag & 23 & 22 & 786 & 1 \\
    WeBid LFI & 1 & 23 & 11,100 & 10\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 984 & 2\\
    .idq access & 14 & 19 & 511 & 2 \\
    /system32/ in URI & 4 & 20 & 1,913 & 4 \\
    Basebuilder LFI & 1 & 22 & 18,133 & 34 \\
    Tomcat Snoop Access & 1 & 24 & 29,830 & 32 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\setlength{\tabcolsep}{8pt}
\begin{table}[h!]
  \footnotesize
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
    UDP Teardrop & 4 & 4 & 4 & 4 & 4 \\
    %%UDP Flood & - & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 3 & 3 & 2\cellcolor{lightgray}$\downarrow$ & 12$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 8$\uparrow$\\        
    JBoss JMX & 45 & 45 & 5\cellcolor{lightgray}$\downarrow$ & 45 & 111$\uparrow$ \\
    scripttag & 1 & 1 & 4$\uparrow$ & 1 & 8$\uparrow$ \\
    WeBid LFI & 10 & 10 & 77$\uparrow$ & 28$\uparrow$ & 32$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 2  & 2 & 2 & 2 & 17$\uparrow$\\
    .idq access & 2  & 2 & 2 & 2 & 12$\uparrow$ \\
    /system32/ in URI & 4  & 4 & 20$\uparrow$ & 1\cellcolor{lightgray}$\downarrow$ & 58$\uparrow$\\
    Basebuilder LFI & 34  & 34 & 117$\uparrow$ & 57$\uparrow$ & 183$\uparrow$\\
    Tomcat Snoop Access & 32  & 32 & 828$\uparrow$ & 2\cellcolor{lightgray}$\downarrow$ & 2564$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 4 \\
    2100384 & 13 & 8 & 18 & 2 \\
    2100399 & 132 & 6 & 3 & 1 \\
    2100401 & 12 & 6 & 25 & 1 \\
    2100402 & 3 & 6 & 12 & 1 \\
    2100408 & 15 & 8 & 9 & 2 \\
    2100485 & 4 & 6 & 3 & 1 \\
    2100486 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 41 & 4\\
    iisadmin access & 3 & 17 & 606 & 1 \\        
    JBoss JMX & 5 & 23 & 925 & 88 \\
    scripttag & 23 & 22 & 2,222 & 1 \\
    WeBid LFI & 1 & 23 & 35,445 & 18\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 853 & 1\\
    .idq access & 14 & 19 & 807 & 1 \\
    /system32/ in URI & 4 & 20 & 1882 & 2 \\
    Basebuilder LFI & 1 & 22 & 60223 & 49 \\
    Tomcat Snoop Access & 1 & 24 & 58,123 & 39 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\setlength{\tabcolsep}{8pt}
\begin{table}[h!]
  \footnotesize
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
    2100384 & 2 & \Fix{} & 2 & 2 & 2 \\
    2100399 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100401 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100402 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100408 & 2 & \Fix{} & 2 & 2 & 2 \\
    2100485 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100486 & 1 & \Fix{} & 1 & 1 & 1 \\
    %%UDP Flood & - & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 4 & 4 & 2\cellcolor{lightgray}$\downarrow$ & 12$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 8$\uparrow$\\        
    JBoss JMX & 88 & 88 & 5\cellcolor{lightgray}$\downarrow$ & 45 & 111$\uparrow$ \\
    scripttag & 1 & 1 & 4$\uparrow$ & 1 & 8$\uparrow$ \\
    WeBid LFI & 18 & 18 & 77$\uparrow$ & 28$\uparrow$ & 32$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 17$\uparrow$\\
    .idq access & 1  & 1 & 1 & 1 & 12$\uparrow$ \\
    /system32/ in URI & 2  & 2 & 20$\uparrow$ & 1\cellcolor{lightgray}$\downarrow$ & 58$\uparrow$\\
    Basebuilder LFI & 49  & 49 & 117$\uparrow$ & 57$\uparrow$ & 183$\uparrow$\\
    Tomcat Snoop Access & 39  & 39 & 828$\uparrow$ & 2\cellcolor{lightgray}$\downarrow$ & 2564$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}
